Semilattice Graphs for Distributed Databases

### 2022-10-03 paper/paper.tex
more stacking!

>>>>

      We can further stack to higher ordinals than $\omega$. Let $n_u \geq 1$ be the number of universes. Let $L_{0, 0}$ be an arbitrary semilattice. Assume we have:

      \begin{align*}
        (l_{u, n}, t_{u, n}) &: \mathrm{SemiFibration}(L_{u, n-1}) & \text{for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u, n} &:= \mathrm{SemiTot}(L_{u, n-1}, l_{u, n}, t_{u, n})    & \text{ for natural $0 \leq u < n_u$, $n \geq 1$ } \\
        L_{u+1, 0} &:= L_{u, \omega} & \text{ for natural $0 \leq u < n_u - 1$ }
      \end{align*}

      where $L_{u, \omega}$ is constructed the same way as $L_{\omega}$ above, as the limit of $L_{u, n}$ as $n$ approaches $\infty$. Inductively, each $L_{u, n}$ is a semilattice for natural $0 \leq u < n_u, n \geq 0$; this lattice's ordinal corresponds to $u \omega + n$. While in theory it may be possible to reach higher ordinals $\omega^2$ and beyond, we consider this beyond the scope of this work.
